Quotient Normalized Maximum Likelihood Criterion for Learning Bayesian Network Structures

### 2018-02-14 main.tex
[hidelinks] added to hyperref
[accepted] options + authot info

\documentclass[twoside]{article}
\usepackage{aistats2018}
\usepackage{amsmath,amsthm,epsfig,booktabs,multirow}
\usepackage{hyperref}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\newcommand{\Le}{\left(}
\newcommand{\Ri}{\right)}

@@

@@

\aistatsauthor{ Author 1 \And Author 2 \And  Author 3 }

\aistatsaddress{ Institution 1 \And  Institution 2 \And Institution 3 } ]

>>>>

\documentclass[twoside]{article}
\usepackage[accepted]{aistats2018}
\usepackage{amsmath,amsthm,epsfig,booktabs,multirow}
\usepackage[hidelinks]{hyperref}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\newcommand{\Le}{\left(}
\newcommand{\Ri}{\right)}

@@

\runningauthor{Tomi Silander, Janne Lepp\"{a}-aho, Elias J\"{a}\"{a}saari, Teemu Roos}

@@

\aistatsauthor{ Tomi Silander$^1$ \And Janne Lepp\"{a}-aho$^{2,4}$ \And Elias J\"{a}\"{a}saari$^{2,3}$ \And Teemu Roos$^{2,4}$   }

\aistatsaddress{ $^1$NAVER LABS Europe \And $^2$Helsinki Institute for \\ Information Technology HIIT \And $^3$Department of CS,\\Aalto University \And $^4$Department of CS,\\University of Helsinki} ]
